Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
Link to plos paper

Wilson suggests that software authors include a `CITATION' file that documents exactly how the
authors of the software would like to be cited by others~\cite{ssi-citation-files}. While this isn't a formal metadata specification (it's not machine
readable for example) this does offer a solution for authors wishing to give explicit instructions to potential citing authors.\dmnote{There is evidence from databases that people actually tend to follow such instructions if they exist: \cite{10.1371/journal.pone.0136631}.} \katznote{added this ref to the introduction - not sure if it is still needed here too}
In a later post on the SSI blog, Jackson gives a good overview of some of the approaches
package authors have taken to automate the generation of citation entities such as bibtex entries~\cite{ssi-how-shalt-i-cite-thee},
and Knepley et al.\ do similarly~\cite{knepley2013accurately}.

>>>>

Wilson suggests that software authors include a `CITATION' file that documents exactly how the
authors of the software would like to be cited by others~\cite{ssi-citation-files}. While this isn't a formal metadata specification (it's not machine
readable for example) this does offer a solution for authors wishing to give explicit instructions to potential citing authors and as noted in the introduction (\S\ref{sec:intro}), there is evidence that authors follow instructions if they exist \cite{10.1371/journal.pone.0136631}.

In a later post on the SSI blog, Jackson gives a good overview of some of the approaches
package authors have taken to automate the generation of citation entities such as bibtex entries~\cite{ssi-how-shalt-i-cite-thee},
and Knepley et al.\ do similarly~\cite{knepley2013accurately}.
